Adopting agile in the large: motivations, success factors and challenges

### 2014-04-23 journal/article.tex
Refactored reasons to change

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        31 &  124 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       155 & 1576 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

-- Few of the primary studies presented a research method. Most of the studies
   were experience reports where the author was a member of the organization
   discussed. Because of this we must assume that the primary studies are
   biased. Due to this risk of bias we chose not to make statistical
   interpretations of the results.

@@

\begin{table}
    \begin{tabular}{ p{1.5cm} l l }
        \toprule
        Reason    &  Examples  &  Sources   \\
        \midrule

        \multicolumn{3}{l}{Demand of improved delivery speed or frequency}  \\
         &  Time To Market must lessen           & x \\
         &  Demand for frequent deliveries       & x \\
         &  Too long cycle time before feedback  & x \\

        \multicolumn{3}{l}{General problems with management of software development} \\
         &  General management dysfunction                & x \\
         &  Problems with motivation and morale           & x \\
         &  Problems coordinating a growing organization  & x \\

        \multicolumn{3}{l}{Demand for flexibility or responsiveness}  \\
         &  Responsiveness to business needs  & x \\
         &  Adaptation as projects evolve     & x \\

        \multicolumn{3}{l}{Problems with overhead and excess in process}  \\
         &  Excess, slowness and costs caused by process  & x \\
         &  The current process is being ignored          & x \\

        \multicolumn{3}{l}{Demand to improve product quality}  \\

        \multicolumn{3}{l}{Problems with planning or keeping schedules}  \\

        \multicolumn{3}{l}{Demand of better customer collaboration}  \\
         &  Customers push for improvement  & x \\

        \multicolumn{3}{l}{Lack of focus or priorities}  \\
         &  Business needs or priorities are not regarded  & x \\
         &  Requirements are not understood                & x \\

        \multicolumn{3}{l}{Communication and collaboration dificulties}  \\
         &  Problems in communication across and within projects  & x \\
         &  Teams work in silos or isolation  & x \\

        \bottomrule
    \end{tabular}
    \caption{Summarizing why large organizations initiate an agile transformation (RQ1)}
    \label{table:reasonstochange}
\end{table}

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. Companies saw it critical to reduce the Time
To Market (TTM) of new features.

>>>>

\begin{table}[h]
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

-- Few of the primary studies presented a research method. Most of the studies
   were experience reports where the author was a member of the organization
   discussed. Because of this we must assume that the primary studies are
   biased. Due to this risk of bias we chose not to make statistical
   interpretations of the results. We only use relative measure when comparing
   results.

@@

\begin{table}
    \begin{tabular}{ p{1.2cm} p{1.2cm} l }
        \toprule
        \multicolumn{3}{l}{Reasons to change}  \\
        \midrule

        \multicolumn{3}{l}{External issues: Need to respond to changes in business}  \\

        &  \multicolumn{2}{l}{Demand for more frequent deliveries} \\
        &  &  Time To Market must lessen  \\
        &  &  Long cycle times are seen as problematic  \\

        &  \multicolumn{2}{l}{Demand for flexibility or responsiveness} \\
        &  &  Demand for responsiveness to changing business needs  \\
        &  &  Adaptation as projects evolve  \\

        &  \multicolumn{2}{l}{Customers demand improvement} \\

        \multicolumn{3}{l}{\rule{0pt}{4ex} Internal issues: Problems in managing software development}  \\

        &  \multicolumn{2}{l}{General problems with management of software development} \\
        &  &  General management dysfunction  \\
        &  &  Problems with motivation and morale  \\
        &  &  Problems coordinating a growing organization  \\

        &  \multicolumn{2}{l}{Problems with overhead and excess in process}  \\
        &  &  Excess, slowness and costs caused by process  \\
        &  &  The current process is being ignored  \\

        &  \multicolumn{2}{l}{Demand to improve product quality}  \\

        &  \multicolumn{2}{l}{Problems with planning or keeping schedules}  \\

        &  \multicolumn{2}{l}{Too long cycle time before feedback}  \\

        \multicolumn{3}{l}{\rule{0pt}{4ex} Communication issues}  \\

        &  \multicolumn{2}{l}{Communication and collaboration dificulties}  \\
        &  &  Problems in communication across and within projects  \\
        &  &  Teams work in silos or isolation  \\

        &  \multicolumn{2}{l}{Requirements engineering issues}  \\
        &  &  Requirements are not understood  \\
        &  &  Unawareness of what is important  \\

        &  \multicolumn{2}{l}{Demand of better customer collaboration}  \\

        \bottomrule
    \end{tabular}
    \caption{Summarizing why large organizations initiate an agile transformation (RQ1).
             The table presents a hierarchial view of reasons for the organization to change.}
    \label{table:reasonstochange}
\end{table}

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. A frequent theme was the desire to reduce Time To Market (TTM).

* TTM, lead time

[P17]
Faster TTM
"BMC decided to introduce a new generation of their own successful products before competitors could."

[P17]
Product needs to be improved quickly.
The deadline is looming (TTM) "Target delivery of the first release was less than a year away"

[P18]
Reduce TTM "Ericsson set a corporate R\&D goal to reduce Time to Market"
Faster cycles became necessary "This forced the PDU to deliver products in much short cycles."

[P18]
Reduction in lead time, increase in responsiveness, "both appealing and necessary" "in our ‘new’ multimedia market place"

[P32]
TTM must be reduced
"BT is facing rapid marketplace changes that require it to radically increase its speed to market."

[P38]
TTM must be improved, to remain competitive
"The market was moving faster than the development group was able to deliver."

[P39]
The TTM needed to be shortened
The testing time needed to be shortened

[P47]
There was a desire to reduce TTM

* Long cycle time is seen as a problem in itself

[P2] They THINK that agile will make them deliver faster

[P8]
There are challenges in achieving faster and more frequent delivery.

[P25]
Long cycle time is seen as a general problem

[P33]
Long cycles is seen as a problem in itself
"the number of releases had slowed to one major release per year"

[P36]
A "small system" needed to be put in place as fast as possible

[P41]
The goal was to "deliver better quality faster"

[P16]
Lack of feedback
"many people in R\&D had not participated in a major release"
Release cycles are too long, which is clearly problematic

[P49]
It takes ``too long to develop''
It takes ``too long to deploy''
Too little assurance that the result will be good in the changing marketplace
"software was taking too long to develop, too long to deploy, and providing too
little assurance that what was either developed or deployed was really going to
ferry the corporation through the tumultuous waters of its marketplace"

* Slowness combined with cost

[P36]
It is realized that development was slow, and needs to be improved
"Business ... felt the all-too-common frustrations with the pace and cost of development."

[P46]
Development is "too slow and too expensive across the board"

* Customers or ``business'' demand shorter cycles

[P23]
Speed of delivery
"Speed of delivery is of the essence – customers are no longer prepared to wait for 18 months or more for solutions to be delivered."

[P39]
Project stakeholders demand "as early releases as possible"

[P46]
Business cared only about speed to value.

[P5]
New solutions must be delivered on a fast schedule
"The engineering team had to deliver rapid incremental improvement."
Software quality needs to be improved.
"Business pressure for rapid improvement was growing."
"The organization would be required to demonstrate significant improvement in a very short timeframe. It was clear traditional software development methodologies simply would not work."

* Length delivery is a problem in the competition

[P11]
"we couldn't do business as usual" --> delivery speed must be increased, to remain competitive

[P19]
Fear of competitors, something must be done
Long release cycles/duration are "an alarming state that could enable competitors to gain market share"

* Faster is better ROI

[P8]
Provide within shorter cycles in order to focus on highest ROI

* Timeliness, accuracy

[P9]
Product deliveries must be timely, to remain competitive

[P15]
The number of releases needed to be increased, for accuracy
